\textsf{Are frontier models superhuman chemists?}

### 2024-03-19 src/tex/authors.tex
feat: add acronyms, fix credits bug, update pipeline
update authors
update authors and prepare confidence score distribution
added safety description
pin env to make embeddings work
set author ordering
clean up credit order
update contributions
make compile and embedding script
update affiliations

\credit{Adrian~Mirza}{0,1,1,0,1,0,0,0,1,0,0,0,0,0}
\credit{Sreekanth~Kunchapu}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Tanya~Gupta}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jan Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Amir Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Lea Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
%ORCID ID:  0000-0002-5968-8706 Affiliation:    Institute for Technical Chemistry and Environmental Chemistry (ITUC) and Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany
\credit{Mara~Wilhemli}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Macjonathan~Oreke}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Benedict~Emoekabu}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Michael~Pieler}{1,0,0,0,0,0,0,0,0,0,0,0,a0,0}
\credit{Aswanth~Krishnan}{0,0,0,0,0,0,0,0,1,0,0,0,0,0}
\credit{Philippe~Schwaller}{1,1,0,1,1,0,0,0,0,1,0,0,0,0}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,0}
\credit{Berend~Smit}{0,0,0,1,0,0,0,0,0,0,0,0,0,0}
\credit{Kevin Maik Jablonka}{1,1,1,1,1,1,1,1,1,1,1,1,1,1}

\author[1,*]{Nawaf~Alampara~\orcidlink{}}

\author[1,*]{Adrian~Mirza~\orcidlink{0000-0003-4033-4235}}

\author[1,*]{Sreekanth~Kunchapu~\orcidlink{0009-0003-5752-0154}}

\author[1]{Lea~Klepsch~\orcidlink{0000-0003-4978-4670}}
\author[1]{Jan~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1]{Jakob~Meyer}
\author[1]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}
\author[1]{Maximilian~Greiner}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}

\author[1]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[ituc]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[dresden]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}
\author[lsmo]{Amir~Elahi}
\author[lsmo]{Berend~Smit~\orcidlink{0000-0003-4653-8562}}

\author[qpi]{Aswanth~Krishnan}

\author[1]{Mara~Willhelmi}

\author[1]{Macjonathan~Oreke}

\author[Occlu]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}

\author[]{Benedict~Emoekabu}

\author[nccrcat,liac]{Tanya~Gupta}

\author[nccrcat,liac]{Philippe~Schwaller~\orcidlink{0000-0003-3046-6576}}

\author[open,stability]{Michael Pieler~\orcidlink{0000-0001-9186-7045}}

\author[1,2, 3]{Kevin~Maik~Jablonka~\orcidlink{0000-0003-4894-4660}}

@@

\affil[lsmo]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Valais, Switzerland.}
\affil[dresden]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[open]{OpenBioML.org}
\affil[stability]{Stability.AI}
\affil[ituc]{Institute for Technical Chemistry and Environmental Chemistry (ITUC) and Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[qpi]{Qpi volta}
\affil[occlu]{Occlutech GmbH, Jena, Germany}

\affil[]{\texttt{mail@kjablonka.com}}
\affil[*]{These authors contributed equally.}

>>>>

% Main contributors
\credit{Adrian~Mirza}{1,1,1,0,1,0,0,0,1,0,1,1,0,1}
\credit{Nawaf~Alampara}{1,1,1,0,1,0,0,0,1,0,1,0,0,1}
\credit{Sreekanth~Kunchapu}{1,1,0,0,1,0,0,0,0,0,1,0,0,1}

% Question contributors
\credit{Benedict~Emoekabu}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Aswanth~Krishnan}{0,0,0,0,0,0,0,0,1,0,0,0,0,0}
\credit{Tanya~Gupta}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Mara~Wilhemli}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Macjonathan~Oreke}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}

% Question answerers
\credit{Mehrdad Asgari}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Amir Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Lea Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jan Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Johanna Schreiber}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,0}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}

% senior authors 
\credit{Michael~Pieler}{1,0,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Philippe~Schwaller}{1,1,0,1,1,0,0,0,0,1,0,0,0,0}
\credit{Kevin Maik Jablonka}{1,1,1,1,1,1,1,1,1,1,1,1,1,1}

\author[1,$\star$]{Adrian~Mirza~\orcidlink{0000-0003-4033-4235}}
\author[1,$\star$]{Nawaf~Alampara~\orcidlink{}}
\author[1,$\star$]{Sreekanth~Kunchapu~\orcidlink{0009-0003-5752-0154}}
\author[]{Benedict~Emoekabu}
\author[qpi]{Aswanth~Krishnan~\orcidlink{0009-0008-2703-5613}}
\author[nccrcat,liac]{Tanya~Gupta}
\author[1]{Mara~Willhelmi}
\author[1]{Macjonathan~Oreke}

\author[cambridge]{Mehrdad~Asgari~\orcidlink{0000-0002-5427-1610}}
\author[1]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[lsmo]{Amir~Elahi}
\author[]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}
\author[1]{Maximilian~Greiner}
\author[1]{Lea~Klepsch~\orcidlink{0000-0003-4978-4670}}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}
\author[ituc, 2]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Jakob~Meyer}
\author[1]{Jan~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}

\author[1]{Johanna Schreiber}
\author[1]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[dresden]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}

% Senior authors
\author[open,stability]{Michael Pieler~\orcidlink{0000-0001-9186-7045}}
\author[nccrcat,liac]{Philippe~Schwaller~\orcidlink{0000-0003-3046-6576}}
\author[1,2, 3]{Kevin~Maik~Jablonka~\orcidlink{0000-0003-4894-4660}}

@@

\affil[lsmo]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Valais, Switzerland.}
\affil[dresden]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[open]{OpenBioML.org}
\affil[stability]{Stability.AI}
\affil[ituc]{Institute for Technical Chemistry and Environmental Chemistry (ITUC), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[qpi]{QpiVolta Technologies Pvt Ltd}
\affil[cambridge]{Department of Chemical Engineering \& Biotechnology, University of Cambridge, Philippa Fawcett Drive, Cambridge CB3 0AS, UK}

\affil[]{\texttt{mail@kjablonka.com}}
\affil[$\star$]{These authors contributed equally.}
